Correlation between different emission channels from an atom inside a leaky driven cavity

### 2019-11-30 newpaper.tex
Add files via upload

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amsfonts,amsmath, amssymb}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
%\usepackage[none]{hyphenat}
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{cite}
\usepackage{physics}
\usepackage{bm}
\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\usepackage{enumitem}
\usepackage{a4wide}
\usepackage{dsfont}
\usepackage{ amssymb }
\usepackage{cite}
\usepackage[rightcaption]{sidecap}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{ragged2e}
\usepackage{pdfpages} 
\usepackage{csquotes}
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Correlation between different emission channels from an atom inside a leaky driven cavity\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
\thanks{corresponding author e-mail: guillermopreisser@hotmail.com}
}

\author{\IEEEauthorblockN{Guillermo Preisser and Pablo Barberis Blostein}
\IEEEauthorblockA{\textit{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas,
} \\
\textit{Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}\\
Dated: 15 August, 2019}
}

\maketitle

@@

%the recent advances?
\section{Introduction}
Spontaneous emission is a phenomenon that has been studied since the
early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
main characteristics of spontaneous emission is that
\fxnote{spontaneus emission no es exponencial, es aproximadamente
  exponencial, si quitas la aproximacion markoviana te queda una cola
  polinomial, quite la oracion} the exact time of emission, as well as
the direction in which the photon is emitted, is random, which
difficults its measurement. On the other hand, photons emitted from a
cavity are easy to measure, partly due the fact that we know that they
leave the cavity through one of the lateral mirrors \cite{326305,
  doi:10.1063/1.113345}. The randomness of the direction in which the
photons are emitted by atoms in free space difficults photon counting
experiments. To sort out this difficulty one could think of a physical
arrangement, in which the two-level atom is coupled to the stimulated
mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this
physical arrangement, \fxnote*{tienes una cita donde lo nombren
  asi?}{which is known as the driven Jaynes-Cummings model}, one could
try to estimate the number of spontaneous emissions of the atom
--which are emitted in modes that are not cavity modes and therefore
escape the cavity-- by measuring the photons that leak through one of
the cavity mirrors. In the case that a
correlation exists between the two quantities, we can count the number
of photons that leak the cavity through its mirror, which is easy to
measure, to find information about the number of photons emitted into
the other modes (spontaneus emission), which are difficult to measure.
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In
    both of these arrangements we consider a source which stimulates
    the atom provoking it to spontaneously emit, once it decays. We
    consider a detector in two directions, and we keep a register of
    the number of photons measured in each direction. (a) In the case
    for the atom we don't expect a correlation between m (the number
    of photons measured in the upper side of the atom) and n (the
    number of photons measured in the right side of the atom); (b) for
    the atom in the cavity (a cavity with some loss rate) we study the
    possibility that the cavity generates a correlation between the
    emissions of the atom and the emissions of the cavity, which
    correspond to the emissions that leak through mirror
    2.}} 
\end{center}
\end{figure*}
\end{center}

@@

This article is organized as follows: A general overview of the driven
Jaynes-Cummings model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain probability distributions
that relate the number of spontaneous and cavity emissions. In section
\ref{sc:correlation} we calculate the correlation between the two variables.
Concluding remarks are given in section \ref{sc:conclusions}

\section{Driven Jaynes-Cummings model}\label{sc:drivenjc}
We consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cavity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume , $d$ is the atomic dipole , and
$\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term
proportional to the coherent field amplitude. Dissipation is
introduced by the following non-hermitian Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, ,
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrumped by spontaneus emission by the atom or when a
photon leaks the cavity.

@@

\begin{subequations}\label{relprob}
  \begin{eqnarray}  \delta p_1 &=& \gamma \bra{\phi
      (t)} \sigma_+
                                                  \sigma_-\ket{\psi (t)}\delta t\, , \\
    \delta p_2 &=& 2\kappa \bra{\phi (t)} a^\dagger a\ket{\psi
                   (t)}\delta t \, .
  \end{eqnarray}
\end{subequations}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the resulting state for this step. One quantum trajectory of
total time $t$ is obtained after repeating the previous procedure
$t/\delta t$ steps. For each trajectory we count the number of quantum
jumps, the jumps correponding to operator $a$ reduces the number of
photons inside the cavity and corresponds to a photon that leak the
cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
unitary evolution and send it back to the ground state, it corresponds
to a spontaneous emission. The procedure to register emissions in the
two different channels is summarized in algorithm \ref{alg1}.

@@

In order to find the value of the cavity drive $\mathcal{E}$ as a
function of the mean value of photons inside the cavity, we solve the
Maxwell-Bloch equations. These equations give the dynamic of our
system for the variables $\expval{a}, \expval{\sigma_-}$ and
$\expval{\sigma_z}$ that correspond to the cavity field, atomic
coherence, and atomic inversion respectively \cite{Alsing_1991}. For
the case of the driven Jaynes-Cummings system, these equations are
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined $z = e^{i\omega t}\expval{a}$,
$v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
When the system is stable, we obtain, from
\eqref{maxbloch}, the steady state
solutions \cite{gagniuc2017markov}
\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} +
  g\expval{\sigma_-}_{ss}}{\kappa}\, ,
\end{equation}
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\, ,
\end{equation}
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1
+ \frac{2g^2}{\gamma \kappa}\frac{1}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2\, .
\end{equation}
When $\gamma \gg g$, the expected value of the number of photons in
the cavity is 
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 \approx \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}

@@

\begin{algorithm}[!t]
\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
\label{alg1}
\begin{algorithmic}
\STATE $N$: number of temporal intervals
\STATE $N_A $: number of spontaneous emissions
\STATE $N_C$: number of cavity emissions
\STATE $N_{max}$: maximum number of cavity emissions
\STATE $N_{CA}$: matrix relating the number of cavity emissions with the number of spontaneous emissions
%\STATE $K [\equiv] contador$

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$

\end{algorithmic}

\end{algorithm}

\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.55]{newerrorppp.pdf}
\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$. In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
\paragraph{The case where the time we measure photons is fixed}

@@

\begin{figure}[!t]  
\centering
\includegraphics[scale = 0.45]{newsigmaeng.pdf}
\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
\label{graph}
\end{figure} 
Having Eq. \eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons. Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig. \ref{probdisult} (a). From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig. \ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions. 
Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig. \ref{graph}.

@@

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.45]{million1.pdf}
\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.45]{million2.pdf}
\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases

@@

\section{Conclusions}\label{sc:conclusions}

Atomic emission in cavity and non-cavity modes of an atom inside a
leaky cavity are correlated. The correlations are produced because the
cavity breaks the markovian behavior of atomic emission. the presence
of correlation between photons measured in different directions is a
signature of non-markovian behaviour. This correlation also allows us
to improve the knowledge we know about the probability distribution of
atomic spontaneus emission if we know the number of photons that leak
the cavity.

@@

\section*{Acknowledgment}

Support by UNAM, projects CONACyT and UNAM PAPIIT IG100518.

\bibliographystyle{IEEEtran}
\bibliography{reftesis}
\end{document}

>>>>

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps, 
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\usepackage[ruled,vlined]{algorithm2e}

\usepackage{physics}
\usepackage{fixme}
%\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Correlation between different emission channels from an atom inside a leaky driven cavity}% Force line breaks with \\

\author{Guillermo Preisser}
 \email{Corresponding author e-mail: guillermo.preisser@uabc.edu.mx}
 %Lines break automatically or can be forced with \\
\author{Pablo Barberis}%
\affiliation{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas, Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

@@

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{INTRODUCTION}

Spontaneous emission is a phenomenon that has been studied since the
early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
main characteristics of spontaneous emission is that
\fxnote{spontaneus emission no es exponencial, es aproximadamente
  exponencial, si quitas la aproximacion markoviana te queda una cola
  polinomial, quite la oracion} the exact time of emission, as well as
the direction in which the photon is emitted, is random, which
difficults its measurement. On the other hand, photons emitted from a
cavity are easy to measure, partly due the fact that we know that they
leave the cavity through one of the lateral mirrors \cite{326305,
  doi:10.1063/1.113345}. The randomness of the direction in which the
photons are emitted by atoms in free space difficults photon counting
experiments. To sort out this difficulty one could think of a physical
arrangement, in which the two-level atom is coupled to the stimulated
mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this
physical arrangement, \fxnote*{tienes una cita donde lo nombren
  asi?}{which is known as the driven Jaynes-Cummings model}, one could
try to estimate the number of spontaneous emissions of the atom
--which are emitted in modes that are not cavity modes and therefore
escape the cavity-- by measuring the photons that leak through one of
the cavity mirrors. In the case that a
correlation exists between the two quantities, we can count the number
of photons that leak the cavity through its mirror, which is easy to
measure, to find information about the number of photons emitted into
the other modes (spontaneus emission), which are difficult to measure.

@@

This article is organized as follows: A general overview of the driven
Jaynes-Cummings model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain probability distributions
that relate the number of spontaneous and cavity emissions. In section
\ref{sc:correlation} we calculate the correlation between the two variables.
Concluding remarks are given in section \ref{sc:conclusions}
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In
    both of these arrangements we consider a source which stimulates
    the atom provoking it to spontaneously emit, once it decays. We
    consider a detector in two directions, and we keep a register of
    the number of photons measured in each direction. (a) In the case
    for the atom we don't expect a correlation between m (the number
    of photons measured in the upper side of the atom) and n (the
    number of photons measured in the right side of the atom); (b) for
    the atom in the cavity (a cavity with some loss rate) we study the
    possibility that the cavity generates a correlation between the
    emissions of the atom and the emissions of the cavity, which
    correspond to the emissions that leak through mirror
    2.}} 
\end{center}
\end{figure*}
\end{center}

\section{Driven Jaynes-Cummings model}\label{sc:drivenjc}
e consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cavity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume , $d$ is the atomic dipole , and
$\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term
proportional to the coherent field amplitude. Dissipation is
introduced by the following non-hermitian Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, ,
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrumped by spontaneus emission by the atom or when a
photon leaks the cavity.

@@

\begin{subequations}\label{relprob}
  \begin{eqnarray}  \delta p_1 &=& \gamma \bra{\phi
      (t)} \sigma_+
                                                  \sigma_-\ket{\psi (t)}\delta t\, , \\
    \delta p_2 &=& 2\kappa \bra{\phi (t)} a^\dagger a\ket{\psi
                   (t)}\delta t \, .
  \end{eqnarray}
\end{subequations}
\makeatletter
%\DeclareCaptionLabelFormat{numberless}{\ALG@name#1}
%\captionsetup[algorithm]{labelformat=numberless} 
\makeatother
\begin{algorithm}
\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
\label{alg1}
\begin{algorithmic}
%\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
\STATE $N$: number of temporal intervals
\STATE $N_A $: number of spontaneous emissions
\STATE $N_C$: number of cavity emissions
\STATE $N_{max}$: maximum number of cavity emissions
\STATE $N_{CA}$: matrix relating the number of cavity emissions with the number of spontaneous emissions

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$
\end{algorithmic}
\end{algorithm}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the resulting state for this step. One quantum trajectory of
total time $t$ is obtained after repeating the previous procedure
$t/\delta t$ steps. For each trajectory we count the number of quantum
jumps, the jumps correponding to operator $a$ reduces the number of
photons inside the cavity and corresponds to a photon that leak the
cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
unitary evolution and send it back to the ground state, it corresponds
to a spontaneous emission. The procedure to register emissions in the
two different channels is summarized in algorithm. \ref{alg1}.

@@

In order to find the value of the cavity drive $\mathcal{E}$ as a
function of the mean value of photons inside the cavity, we solve the
Maxwell-Bloch equations. These equations give the dynamic of our
system for the variables $\expval{a}, \expval{\sigma_-}$ and
$\expval{\sigma_z}$ that correspond to the cavity field, atomic
coherence, and atomic inversion respectively \cite{Alsing_1991}. For
the case of the driven Jaynes-Cummings system, these equations are
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined $z = e^{i\omega t}\expval{a}$,
$v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
When the system is stable, we obtain, from
\eqref{maxbloch}, the steady state
solutions \cite{gagniuc2017markov}
\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.7]{newerrorppp.pdf}
\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$. In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} +
  g\expval{\sigma_-}_{ss}}{\kappa}\, ,
\end{equation}
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\, ,
\end{equation}
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1
+ \frac{2g^2}{\gamma \kappa}\frac{1}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2\, .
\end{equation}
When $\gamma \gg g$, the expected value of the number of photons in
the cavity is 
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 \approx \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}

@@

\begin{figure}[!b]  
\centering
\includegraphics[scale = 0.5]{newsigmaengg.pdf}
\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
\label{graph}
\end{figure}

\paragraph{The case where the time we measure photons is fixed}

@@

Having Eq. \eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons. Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig. \ref{probdisult} (a). From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig. \ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions. 
Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig. \ref{graph}.

@@

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.5]{million1.pdf}
\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.5]{million2.pdf}
\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.5]{ccorr1.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = \kappa =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.5]{cnocorr1.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma = \kappa =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}

@@

\section{Conclusions}\label{sc:conclusions}
Atomic emission in cavity and non-cavity modes of an atom inside a
leaky cavity are correlated. The correlations are produced because the
cavity breaks the markovian behavior of atomic emission. the presence
of correlation between photons measured in different directions is a
signature of non-markovian behaviour. This correlation also allows us
to improve the knowledge we know about the probability distribution of
atomic spontaneus emission if we know the number of photons that leak
the cavity.

@@

\bibliography{reftesis}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file apssamp.tex ******
